Colonies - Compute Continuums across Platforms

### 2023-04-13 paper_2023/paper.tex
second draft2

The primary objective of the Colonies framework is to offer uninterrupted access to computing resources, without interruptions or limitations, as data flows from one service to another. To establish such seamless compute continuums, the paper introduces Colonies, a \emph{decentralized runtime environment} designed to integrate with third-party systems to create a seamlessly integrated computing ecosystem. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where workflows can be decomposed into independent microservices that can easily be integrated with other systems or applications running anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems across platforms.

@@

In summary, the primary objective of Colonies is to offer uninterrupted access to computing resources, without interruptions or limitations, as data flows from one service to another. Achieving seamless compute continuum requires development of simple, secure, scalable, and robust solutions. Colonies serves as an initial step towards realizing this vision of a seamlessly integrated computing ecosystem.

>>>>

The primary objective of the Colonies framework is to offer uninterrupted access to computing resources, without interruptions or limitations, allowing data to flow from one service to another. To establish such seamless compute continuums, the paper introduces Colonies, a \emph{decentralized runtime environment} designed to easily integrate with third-party systems to create a seamlessly integrated computing ecosystem. Colonies is built around a loosely-coupled microservices architecture that separates workflow definitions from implementation and deployment. The primary objective is to establish a platform where workflows can be decomposed into independent microservices that can easily be integrated with other systems or applications running anywhere on the Internet. The remainder of the paper describes the Colonies framework and how it can be used to create robust and scalable AI systems across platforms.

@@

In summary, the primary objective of Colonies is to offer uninterrupted access to computing resources, allowing data to flow from one service to another. Achieving seamless compute continuum requires development of simple, secure, scalable, and robust solutions. Colonies serves as an initial step towards realizing the vision of a seamlessly integrated computing ecosystem.
